\documentclass[12pt,reqno]{amsart}
\usepackage{array,arydshln}
\usepackage{amsfonts,amssymb,amsmath,amsthm,
            amssymb,amsopn,amsxtra,amstext,amsbsy}
\usepackage{subfig} % To add subfigures
\usepackage[makeroom]{cancel}
%%\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{array}
\usepackage{url}
\usepackage[spanish]{babel}
\usepackage{color}
%\usepackage{float}
\usepackage{savesym}
\savesymbol{AND}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{enumerate}
\newtheorem*{myteo}{Teorema}
\newtheorem*{mydef}{Definici\'on}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\def\R{{\mathbb R }}
\def\N{{\mathbb N }}
\voffset=-10mm
\oddsidemargin=0pt 
\evensidemargin=0pt
\topmargin=-10mm
\headsep=10mm
\headheight=18pt 
\footskip=30pt
\topskip=0mm
\textwidth 167mm
\textheight=230mm
\parindent=5mm 
\marginparsep=3mm
\marginparwidth=19mm
%\renewcommand{\baselinestretch}{2} %double spacing
\vfuzz2pt % Don't report over-full v-boxes if over-edge is small
\hfuzz6pt % Don't report over-full h-boxes if over-edge is small

%% MYREMARK ENVIRONMENT %%%%%%%%%%%
\newenvironment{mycolor}{\color{red}}{}
\newcounter{myremarkcount}
\setcounter{myremarkcount}{0}
\newsavebox{\myremarkbox}
\newenvironment{myremark}
{% This is the begin code
\medskip
\begin{flushright}
\begin{lrbox}{\myremarkbox}%
\begin{minipage}[t]{0.9\linewidth}
\stepcounter{myremarkcount}
\footnotesize
\begin{mycolor}
{\bf Remark \arabic{myremarkcount}.}
\begin{it}
}
{% This is the end code
\end{it}
\end{mycolor}
\end{minipage}
\end{lrbox}
\fbox{\usebox{\myremarkbox}}
\end{flushright}

\bigskip}


\addtolength{\itemsep}{1.5\baselineskip}

\title{An Online  Vector error correction model for forecasting exchange rates}
\author[P. Arce]{Paola Arce}
\address[Paola Arce]{Departamento de Inform\'atica, UTFSM}
\email{paola.arce@usm.cl}
\author[W. Kristjanpoller]{Werner Kristjanpoller} 
\address[Werner Kristjanpoller]{Departamento de Industrias, UTFSM}
\email{werner.kristjanpoller@usm.cl}
\author[L. Salinas]{Luis Salinas}
\address[Luis Salinas]{Departamento de Inform\'atica, UTFSM \and CCTVal, UTFSM}
\email{luis.salinas@usm.cl}


\begin{document}

\maketitle

\begin{abstract}
Foreign exchange rates have been studied as a set of economic
variables whose relationship is said to be cointegrated. When
cointegration exists there are several models which attempt to predict
their future behaviour using historical information. In particular,
vector error correction (VEC) model is an econometric time series
framework widely used to characterize the joint dynamic behaviour of a
set of cointegrated variables. VEC is a particular case of the vector
autoregression (VAR) model that models a set of any variables
capturing linear interdependence among them.  As well as VAR and VEC
model parameters are obtained using the ordinary least squares (OLS)
method.  Even though OLS is extensively used, it has over-fitting
issues and is computationally expensive.  Due to the amount of new
information available in foreign exchange markets, the using of VAR
and VEC models is not suitable in online contexts.  In this article we
present a new model able to obtain VEC parameters faster which are
less adjusted to the data. Our model can be used in online contexts
due to its reduced the response time and because it considers a
portion of the historical data.
\end{abstract} 

\input{src/intro}
\input{src/varvec}
\input{src/OLS}
\input{src/RR}
\input{src/refinements}
\input{src/lambda}
\input{src/onlinemodels}
\input{src/model}
%\input{src/onlinevec}
\input{src/data}
%\input{src/experiments}
%\input{src/conclusions}
\input{src/appendix}

\bibliographystyle{IEEEtran}
\bibliography{reference}

\end{document}
