\section{Introduction}
\label{sec:introduction}
In finance, it is common to find variables with long-run equilibrium
relationships. This is termed cointegration and reflects the idea that
some sets of variables cannot wander too far from each other. Cointegration
means that one or more linear combinations of these variables are stationary
even though individually they are not. Some models,
such as the Vector Error Correction (VECM) \cite{engle87}, take advantage of
this property and describe the joint behaviour of several cointegrated
variables. VECM introduces this long-run relationship among a set of cointegrated
time series as an error correction term. These time series must be integrated of order 1, denoted I(1), i.e. they become stationary at their first differences. In finance, I(1) time series are very common and 
to introduce cointegration restrictions in models often improves forecasting \cite{duy1998}. Therefore, VECM has been widely adopted in
financial applications \cite{mukherjee1995,seong2013,maysami2000,arestis2001} such as pair trading \cite{herlemont2003} or models with more than two variables \cite{mukherjee1995,engle2004}.

VECM parameters are obtained using the ordinary least squares
(OLS) method \cite{golub1980}. Since OLS involves many calculations, the parameter estimation is computationally expensive when the number of lagged values and
data increases. Moreover, obtaining cointegration vectors 
is also an expensive routine. This is a main limitation to use VECM with stream data with high frequency.
Chen and Lung's BVECM \cite{chen2003} addresses the advantage of distributed processing over conventional rolling window processing. 

Our aims were to study if a parallel version of VECM can be used with high frequency stream data.
Our approach was to determine adaptively the number of observations and lags of VECM which
maximise cointegration relations in the past. 
 This search is computationally
expensive because the Johansen
method \cite{johansen1995} is required to find cointegration vectors, which is of order $O(n^3)$. Therefore, our proposal, called Adaptively Vector Error Correction (AVECM), 
is to parallelise this search in order to get new parameters before new data arrives.
Model effectiveness is focused on out-of-sample forecast rather than in-sample
fitting. This criterion allows AVECM prediction capability to be
expressed rather than just explaining data history.
The forecast capability of our method was measured using MSE and the Theil's $U$-statistic \cite{theil1966} widely used in economic forecast. Tests were run using four currency rates: Euro (EUR) to
United States Dollar (USD) (EURUSD), British Pound (GBP) to USD (GBPUSD), USD to Swiss
Franc (CHF) (USDCHF) and USD to Japanese Yen (JPY) (USDJPY) with a 10-seconds frequency.

This paper is organised as follows: section \ref{sec:background} presents the
VAR and VECM, the AVECM algorithm is presented in section \ref{sec:methodology}.
In section \ref{sec:results} we describe the tests carried on to assess the
accuracy and the execution time of AVECM.  This section also includes a
description of the test data.  Section \ref{sec:conclusions} contains the
conclusions and a discussion of future research.
